Notes on Semi-Supervised `Novelty Detection'

### 2011-04-27 semisupervised/notes.tex
Some stuff

\subsection{Dora with world model}
\label{sec:dora-experiment}

@@

Nonetheless to build that optimal detector we need information on $P(x)$ which often is not available.
We focus then on the study of the bias introduced by using $P(x|k)$ as a threshold.
For that we compared all roc curves based on perfect information for each missing
classes (\autoref{fig:roc-curves-missing-1}).

@@

\begin{figure}
\missingfigure[figwidth=\textwidth]{}

\caption{\label{fig:confusion-matrix-dora}Confusion matrix for the 11 classes that make up the dora distribution.}
\end{figure}

@@

@@

\subsubsection{Approximation Models}

In this section, I should describe how we use graphical models to model both $P(x|k)$ and $P(x)$.
And made them as $P(G)$ and $P(G')$.

@@

\subsection{How Dora models the world?}
\label{sec:dora-models}

>>>>

\clearpage
\subsection{Dora with world model}
\label{sec:dora-experiment}

@@

Nonetheless to build that optimal detector we need information on $P(x)$ which often is not available.
We focus then on the study of the bias introduced by only using $P(x|k)$ as a threshold.

For that we compared all roc curves based on perfect information for each missing
classes (\autoref{fig:roc-curves-missing-1}).

@@

@@

These are 
\begin{figure}
\missingfigure[figwidth=\textwidth]{}
\caption{\label{fig:confusion-matrix-dora}Confusion matrix for the 11 classes that make up the dora distribution.}
\end{figure}

@@

\subsubsection{Modeling the World with Graphical Models}
The previous experiences assume perfect knowledge on the probability distributions functions.
This sections presents how Dora models those distributions and how to perform
novelty detection with them.

Dora uses \emph{probabilistic graphical models} to represent all extracted knowledge from the world.
Those allow to easily model certain probabilistic properties such as conditional independence.
And easy the process of several computational problems on the distributions.
Several tools exists for this type of graphical manipulation such as: \emph{Bayesian networks}, \emph{Markov Random Fields}
or \emph{Factor Graphs}.

Dora underlying graphical methods are based on \emph{Factor Graphs}\citep{kschischang2001factor}, which are bipartites graph composed of variable and factor nodes representing the random variables and several factor functions between the variables that are used to decomposed the distribution.

\begin{figure}
Graphical model of Dora
\end{figure}

We will use $P(G)$.

We will try to 
In this section, I should describe how we use graphical models to model both $P(x|k)$ and $P(x)$.
And made them as $P(G)$ and $P(G')$.

@@

\clearpage
\subsection{How Dora models the world?}
\label{sec:dora-models}
